---
title: "NormEvidenceInterventions"
author: "Aaron Dantzler"
date: "2023-07-17"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data Processing

```{r}

library(readxl)

file_path <- "D:\\Princeton\\BSPL\\Norm Interventions\\nabnexus\\allwaves.xlsx"

dataframe <- read_excel(file_path)

```

```{r}

dataframe <- dataframe[-nrow(dataframe), ]

```


```{r}

library(dplyr)

new_df <- select(dataframe, prolific, control, treatment, b_frq_topic_t1, 
                 b_frq_t1, importance_t1_1, importance_t1_2, importance_t1_3, 
                 importance_t1_4, importance_t1_5, importance_t1_6, 
                 b_frq_topic_t2, b_frq_t2, importance_t2_1, importance_t2_2, 
                 importance_t2_3, importance_t2_4, importance_t2_5, 
                 importance_t2_6, b_frq_topic_t3, b_frq_t3, importance_t3_1, 
                 importance_t3_2, importance_t3_3, importance_t3_4, 
                 importance_t3_5, importance_t3_6)

```

```{r}

library(stringr)

new_df$frq_t1_character_count <- nchar(new_df$b_frq_t1)

new_df$frq_t1_word_count <- str_count(new_df$b_frq_t1, "\\S+")

new_df$frq_t2_character_count <- nchar(new_df$b_frq_t2)

new_df$frq_t2_word_count <- str_count(new_df$b_frq_t2, "\\S+")

new_df$frq_t3_character_count <- nchar(new_df$b_frq_t3)

new_df$frq_t3_word_count <- str_count(new_df$b_frq_t3, "\\S+")

```

```{r}

new_df <- select(new_df, prolific, control, treatment, b_frq_topic_t1, 
                 b_frq_t1, frq_t1_character_count, frq_t1_word_count,
                 importance_t1_1, importance_t1_2, importance_t1_3, 
                 importance_t1_4, importance_t1_5, importance_t1_6, 
                 b_frq_topic_t2, b_frq_t2, frq_t2_character_count,
                 frq_t2_word_count, importance_t2_1, importance_t2_2, 
                 importance_t2_3, importance_t2_4, importance_t2_5, 
                 importance_t2_6, b_frq_topic_t3, b_frq_t3, 
                 frq_t3_character_count, frq_t3_word_count, importance_t3_1, 
                 importance_t3_2, importance_t3_3, importance_t3_4, 
                 importance_t3_5, importance_t3_6)

```

```{r}

new_df <- rename(new_df, frq_topic_t1 = b_frq_topic_t1, frq_t1 = b_frq_t1,
                 frq_topic_t2 = b_frq_topic_t2, frq_t2 = b_frq_t2,
                 frq_topic_t3 = b_frq_topic_t3, frq_t3 = b_frq_t3)

```

# Regressing Chosen Topic ~ Topic Importance

## This includes regressions for each time period as well as one for everything combined.

```{r}

library(nnet)

# Multinomial Logistic Regression 
model <- multinom(frq_topic_t1 ~ importance_t1_1 + importance_t1_2 + 
                          importance_t1_3 + importance_t1_4 + importance_t1_5 +
                          importance_t1_6, data = new_df)

summary(model)

```

```{r}

# Multinomial Logistic Regression 
model <- multinom(frq_topic_t2 ~ importance_t2_1 + importance_t2_2 + 
                          importance_t2_3 + importance_t2_4 + importance_t2_5 +
                          importance_t2_6, data = new_df)

summary(model)

```

```{r}

# Multinomial Logistic Regression 
model <- multinom(frq_topic_t3 ~ importance_t3_1 + importance_t3_2 + 
                          importance_t3_3 + importance_t3_4 + importance_t3_5 +
                          importance_t3_6, data = new_df)

summary(model)

```

```{r}

frq_topic <- c(new_df$frq_topic_t1, new_df$frq_topic_t2, new_df$frq_topic_t3)

importance_1 <- c(new_df$importance_t1_1, new_df$importance_t2_1, 
                  new_df$importance_t3_1)

importance_2 <- c(new_df$importance_t1_2, new_df$importance_t2_2, 
                  new_df$importance_t3_2)

importance_3 <- c(new_df$importance_t1_3, new_df$importance_t2_3, 
                  new_df$importance_t3_3)

importance_4 <- c(new_df$importance_t1_4, new_df$importance_t2_4, 
                  new_df$importance_t3_4)

importance_5 <- c(new_df$importance_t1_5, new_df$importance_t2_5, 
                  new_df$importance_t3_5)

importance_6 <- c(new_df$importance_t1_6, new_df$importance_t2_6, 
                  new_df$importance_t3_6)

stacked_df <- data.frame(frq_topic, importance_1, importance_2, importance_3,
                         importance_4, importance_5, importance_6)

```

```{r}

# Multinomial Logistic Regression 
model <- multinom(frq_topic ~ importance_1 + importance_2 + 
                          importance_3 + importance_4 + importance_5 +
                          importance_6, data = stacked_df)

summary(model)

```
## The interpretation of all of these regressions is that the higher the respondent ranks the importance of a topic, the more likely they are to choose it, which makes sense.

# Regressing Chosen Topic ~ Time

## Data Processing 

```{r}

time1 <- c(1)
num_repetitions <- 616
time1 <- rep(time1, times = num_repetitions)

time2 <- c(2)
time2 <- rep(time2, times = num_repetitions)

time3 <- c(3)
time3 <- rep(time3, times = num_repetitions)

time <- c(time1, time2, time3)

stacked_df$time <- time

```

```{r}

# Multinomial Logistic Regression 
model <- multinom(frq_topic ~ time, data = stacked_df)

summary(model)

```
## Time does not seem to have a relationship with chosen topic.

# Regressing Topic Importance ~ Time

```{r}

model <- lm(importance_1 ~ time, data = stacked_df)

summary(model)

```

```{r}

model <- lm(importance_2 ~ time, data = stacked_df)

summary(model)

```

```{r}

model <- lm(importance_3 ~ time, data = stacked_df)

summary(model)

```

```{r}

model <- lm(importance_4 ~ time, data = stacked_df)

summary(model)

```

```{r}

model <- lm(importance_5 ~ time, data = stacked_df)

summary(model)

```

```{r}

model <- lm(importance_6 ~ time, data = stacked_df)

summary(model)

```
## Time does not seem to effect the importance of each topic.

# Regressing Chosen Topic on Treatment

## Data Processing

```{r}

control <- new_df$control
num_repititions <- 3
control <- rep(control, times = num_repititions)

treatment <- new_df$treatment
treatment <- rep(treatment, times = num_repititions)

stacked_df$control <- control
stacked_df$treatment <- treatment

```

```{r}

stacked_df$climatenorm <- ifelse(stacked_df$control != "climate" & 
                                   stacked_df$treatment == "norm", 1, 0)

stacked_df$climateevidence <- ifelse(stacked_df$control != "climate" & 
                                   stacked_df$treatment == "evidence", 1, 0)

stacked_df$climatenormevidence <- ifelse(stacked_df$control != "climate" & 
                                   stacked_df$treatment == "normevidence", 1, 0)

stacked_df$healthnorm <- ifelse(stacked_df$control != "health" & 
                                   stacked_df$treatment == "norm", 1, 0)

stacked_df$healthevidence <- ifelse(stacked_df$control != "health" & 
                                   stacked_df$treatment == "evidence", 1, 0)

stacked_df$healthnormevidence <- ifelse(stacked_df$control != "health" & 
                                   stacked_df$treatment == "normevidence", 1, 0)

stacked_df$politicsnorm <- ifelse(stacked_df$control != "politics" & 
                                   stacked_df$treatment == "norm", 1, 0)

stacked_df$politicsevidence <- ifelse(stacked_df$control != "politics" & 
                                   stacked_df$treatment == "evidence", 1, 0)

stacked_df$politicsnormevidence <- ifelse(stacked_df$control != "politics" & 
                                   stacked_df$treatment == "normevidence", 1, 0)

```

## 1-2: Climate, 3-4: Health, 5-6: Politics

```{r}

model <- lm(importance_1 ~ climatenorm + climateevidence + climatenormevidence +
              healthnorm + healthevidence + healthnormevidence + politicsnorm +
              politicsevidence + politicsnormevidence, data = stacked_df)

summary(model)

```

```{r}

model <- lm(importance_2 ~ climatenorm + climateevidence + climatenormevidence +
              healthnorm + healthevidence + healthnormevidence + politicsnorm +
              politicsevidence + politicsnormevidence, data = stacked_df)

summary(model)

```

```{r}

model <- lm(importance_3 ~ climatenorm + climateevidence + climatenormevidence +
              healthnorm + healthevidence + healthnormevidence + politicsnorm +
              politicsevidence + politicsnormevidence, data = stacked_df)

summary(model)

```

```{r}

model <- lm(importance_4 ~ climatenorm + climateevidence + climatenormevidence +
              healthnorm + healthevidence + healthnormevidence + politicsnorm +
              politicsevidence + politicsnormevidence, data = stacked_df)

summary(model)

```

```{r}

model <- lm(importance_5 ~ climatenorm + climateevidence + climatenormevidence +
              healthnorm + healthevidence + healthnormevidence + politicsnorm +
              politicsevidence + politicsnormevidence, data = stacked_df)

summary(model)

```

```{r}

model <- lm(importance_6 ~ climatenorm + climateevidence + climatenormevidence +
              healthnorm + healthevidence + healthnormevidence + politicsnorm +
              politicsevidence + politicsnormevidence, data = stacked_df)

summary(model)

```
## For importance_1, we expect climatenorm, climateevidence, and climatenormevidence to increase importance_1 and so on for the other topics. However, we do not see this relationship. 

```{r}

# Multinomial Logistic Regression 
model <- multinom(frq_topic ~ climatenorm + climateevidence + 
                    climatenormevidence + healthnorm + healthevidence +
                    healthnormevidence + politicsnorm + politicsevidence + 
                    politicsnormevidence, data = stacked_df)

summary(model)

```

### Baseline is Climate Control, Evidence Control

```{r}

# Multinomial Logistic Regression 
model <- multinom(frq_topic ~ control + control:treatment, data = stacked_df)

summary(model)

```

## Data Processing

```{r}

stacked_df$importance <- ifelse(stacked_df$frq_topic == "1", stacked_df$importance_1,
                        ifelse(stacked_df$frq_topic == "2", stacked_df$importance_2,
                               ifelse(stacked_df$frq_topic == "3", stacked_df$importance_3,
                                      ifelse(stacked_df$frq_topic == "4", stacked_df$importance_4,
                                             ifelse(stacked_df$frq_topic == "5", stacked_df$importance_5,
                                                    ifelse(stacked_df$frq_topic == "6", stacked_df$importance_6, NA))))))

```

# Regressing Topic Chosen on Topic Importance

```{r}

# Multinomial Logistic Regression 
model <- multinom(frq_topic ~ importance, data = stacked_df)

summary(model)

```

```{r}

stacked_df$t1_treated <- ifelse(stacked_df$control == "climate", 0, 1)
stacked_df$t2_treated <- ifelse(stacked_df$control == "climate", 0, 1)

stacked_df$t3_treated <- ifelse(stacked_df$control == "health", 0, 1)
stacked_df$t4_treated <- ifelse(stacked_df$control == "health", 0, 1)

stacked_df$t5_treated <- ifelse(stacked_df$control == "politics", 0, 1)
stacked_df$t6_treated <- ifelse(stacked_df$control == "politics", 0, 1)

```

```{r}

# Multinomial Logistic Regression 
model <- multinom(frq_topic ~ t1_treated + t2_treated + t3_treated + 
                    t4_treated + t5_treated + t6_treated, data = stacked_df)

summary(model)

```
## For this regression, we expect to see t2_treated to significantly predict topic 1 and 2 treated and so on. However, we do not see this relationship.

```{r}

# file_path <- "D:\\Princeton\\BSPL\\norms.csv"

# write.csv(new_df, file = file_path, row.names = FALSE)

```
